Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-06-06 paper.Rmd
sfs
sdfasdf

# Results of the updated replication

@@

Table \ref{tab:table2-fixed} shows our replication of B&S Table 2 with (1) regular, not smoothed, AUC-ROC, (2) fixed "Weighted by PITF" and "PITF Split-Population" models, and (3) AUC-ROC values computed on the common joint subset of tests cases that all models have non-missing predictions for. Table \ref{tab:table2-full} further below shows AUC-ROC values for both smoothed and non-smoothed versions, and both the original, model-varying test cases sets and our common joint subset.

@@

B&S interpret the results as follows, on page 20:^[We list the "Overall, ..." interpretation out of order, last, for clarity.]

@@

It performs roughly on par with the Escalation Only model.

One finding that remains is that the "PITF Only" model is outperformed by the "Escalation Only" model. As the former only uses annual inputs, but the data at hand are the 1-month or 6-months level, this is not surprising.

@@

The most straightforward method of incorporating the annual, structural PITF variables--adding them to the predictors of the Escalation RF model--strictly outperforms the Escalation Only model. Note that the two other combination models considered are both non-standard, and that the "PITF Split Population" model does not in fact actually incorporate structural information at all. We thus conclude that adding structural variables actually clearly improves predictive performance.

@@

The use of smoothed ROC curves to calculate AUC-ROC values only clearly benefits the escalation model, it does so consistently, and by a considerable margin. All eight alternative models reported in Tables 1 and 2 do not on average gain when using smoothed ROC curves to calculate AUC.

@@

>>>>

# Results of the updated replication
We now turn to an examination of our replication that fixes the above issues.  The bottom line is that the changes we make turn on their heads the conclusions of B&S.

@@

Table \ref{tab:table2-fixed} shows our replication of B&S Table 2 with (1) regular, not smoothed, AUC-ROC, (2) fixed "Weighted by PITF" and "PITF Split-Population" models, and (3) AUC-ROC values computed on the common, joint subset of tests cases that all models have non-missing predictions for. Table \ref{tab:table2-full} further below shows AUC-ROC values for both smoothed and non-smoothed versions, and both the original, model-varying test cases sets and our common joint subset.

@@

B&S interpret their results as follows, on page 20 and we comment on the conclusions seratim:^[We list the "Overall, ..." interpretation out of order, last, for clarity.]

@@

The weighted model performs roughly on par with the Escalation Only model. One finding that remains is that the "PITF Only" model is outperformed by the "Escalation Only" model. As the former only uses annual inputs, but the data at hand are the 1-month or 6-months level, this is neither surprising, nor noteworthy.

@@

The most straightforward method of incorporating the annual, structural PITF variables--adding them to the predictors of the Escalation RF model--strictly outperforms the Escalation Only model. Note that the two other combination models considered are both non-standard and that the "PITF Split Population" model does not in fact actually incorporate structural information at all. We thus conclude that adding structural variables improves predictive performance.

@@

The use of smoothed ROC curves to calculate AUC-ROC values clearly benefits \textbf{only} the escalation model. It does so consistently and by a considerable margin. All eight alternative models reported in Tables 1 and 2 on average do not gain when using smoothed ROC curves to calculate AUC.

@@

THIS SECTION IS EMPTY
